---
title: "Attitude Regression"
output:
  html_document: default
  html_notebook: default
---

Import 'attitude' dataset
```{r}
data(attitude)
```

plot boxplot for all columns
```{r}
boxplot(attitude)
```

We observe that there are outliers in critical and advance.
We take the boxplot stats for the two columns
```{r}
boxplot.stats(attitude$critical)
```
The outlier here is the value 49
```{r}
boxplot.stats(attitude$advance)
```
The outlier is the value 72

In attitude$critical we will identify the position of the value 49.
```{r}
which(attitude$critical<54)
```
The outlier 49 is in the 6th column

In attitude$advance we will identify the position of the value 72.
```{r}
which(attitude$advance>63)
```
The outlier 72 is in the 26th column

We will interpolate these values with the nearby values

```{r}
attitude$critical[6]<-attitude$critical[7]
attitude$advance[26]<-attitude$advance[27]
```

Now the new dataset is 
```{r}
attitude
```
The new boxplot is 
```{r}
boxplot(attitude)
```
There are no outliers here

Now running regression model on the attitude dataset
```{r}
model<-lm(rating~complaints+privileges+learning+raises+critical+advance, data = attitude)

```

Low taking the summary of this model
```{r}
summary(model)
```

From the above results we see that only attitude$complaints is significant at 1% interval. We reject the null hypothesis. t-value 4.013>2.807(from t-table, df = 30-7, 99% confidence level) 

The F-value is 10.1 which is significant as > 5.65 at 0.1% as per the F stats table. Hence null hypothesis is rejected.

The model explains the data upto 72.5%. Since this has multiple independent variables, we go with the Adjusted R-sq which is 0.6532 i.e 65.32% variation in 'rating' can be explained by model. 
